Using the internal language of toposes in algebraic geometry

### 2014-06-18 poster.tex
Height of the block captions

@@

\newlength{\inboxwd}
\newlength{\iinboxwd}
\newlength{\inboxrule}
\setbeamertemplate{block alerted begin}
{
  \par\vskip\medskipamount
  \begin{beamercolorbox}[sep=0ex,rounded=true,center,dp={2.4ex}]{block alerted title}
    \vskip0cm
    \usebeamerfont{block title}\large\insertblocktitle
  \end{beamercolorbox}
  {\parskip0pt\par}
  \usebeamerfont{block body}
  \vskip-0.8cm
  \begin{beamercolorbox}[sep=0.5cm, rounded=true,center]{block alerted title}
  \setlength{\inboxwd}{\linewidth}
  \addtolength{\inboxwd}{-1cm}
  \begin{beamercolorbox}[rounded=true,wd={\inboxwd},center]{block alerted body}
  \setlength{\iinboxwd}{\inboxwd}
  \setlength{\inboxrule}{\inboxwd}
  \addtolength{\iinboxwd}{-0.5cm}
  \addtolength{\inboxrule}{0.5cm}
  \begin{center}
  \begin{minipage}{\iinboxwd}
  \justifying
}

\setbeamertemplate{block alerted end}
{
  \end{minipage}
  \end{center}
  \end{beamercolorbox}
  \end{beamercolorbox}
  \vskip\smallskipamount
}

>>>>

\makeatletter
\newenvironment{beamercolorboxA}[2][]{%
  \begingroup%
    \def\beamer@colbox@coladd{0pt}%
    \def\beamer@vmode{\leavevmode}%
    \setkeys{beamercolbox}{%
      wd=\textwidth,ht={},dp={},%
      leftskip=0pt,rightskip=0pt plus1fil,%
      sep=0pt,colsep=0pt,colsep*=0pt,%
      shadow=false,rounded=false,ignorebg=false}%
    \setkeys{beamercolbox}{#1}%
    \ifbeamercolorempty[bg]{#2}{\@tempswafalse}{\@tempswatrue}%
    \ifbeamer@colbox@ignorebg\@tempswafalse\fi%
    \def\beamer@colbox@color{#2}%
    \hsize=\beamer@colbox@wd%
    \setbox\beamer@tempbox=\hbox\bgroup\vbox\bgroup%
      \leftskip=\beamer@colbox@ls%
      \advance\leftskip by\beamer@colbox@sep%
      \rightskip=\beamer@colbox@rs%
      \advance\rightskip by\beamer@colbox@sep%
      \ifbeamer@colbox@ignorebg%
        \colorlet{beamer@temp@color}{bg}%
        \usebeamercolor[fg]{#2}%
        \colorlet{bg}{beamer@temp@color}%
      \else%
        \usebeamercolor[fg]{#2}%
      \fi%
      \if@tempswa%
        \advance\leftskip by\beamer@colbox@colsep%
        \advance\rightskip by\beamer@colbox@colsep%
        \ifdim\beamer@colbox@colsep=0pt\else\vskip\beamer@colbox@colsep\fi%
        \ifdim\beamer@colbox@colseps=0pt\else\vskip\beamer@colbox@colseps\fi%
      \fi%
      \ifdim\beamer@colbox@sep=0pt\else\vskip-0.3cm\fi%
      \beamer@vmode\ignorespaces}{%
      \ifdim\beamer@colbox@sep=0pt\else\vskip\beamer@colbox@sep\fi%
      \if@tempswa\ifdim\beamer@colbox@colsep=0pt\else\vskip\beamer@colbox@colsep\fi\fi%
      \if@tempswa\ifdim\beamer@colbox@colseps=0pt\else\vskip\beamer@colbox@colseps\fi\fi%
    \egroup\egroup%
    \wd\beamer@tempbox=\hsize%
    \@tempdima=\wd\beamer@tempbox%
    \ifx\beamer@colbox@ht\@empty%
    \else%
      \ht\beamer@tempbox=\beamer@colbox@ht%
    \fi%
    \ifx\beamer@colbox@dp\@empty%
    \else%
      \dp\beamer@tempbox=\beamer@colbox@dp%
    \fi%
    \ifbeamer@colbox@rounded%
      \if@tempswa%
        \begin{beamerboxesrounded}[%
          shadow=\beamer@colbox@shadow,%
          lower=\beamer@colbox@color,%
          upper=normal text,%
          width=\beamer@colbox@wd]{}%
          \box\beamer@tempbox%
        \end{beamerboxesrounded}%
      \else%
        \ifdim\@tempdima>\textwidth%
          \setbox\beamer@tempbox=\hbox to\textwidth{\hss\box\beamer@tempbox\hss}%
        \fi%
        \box\beamer@tempbox%
      \fi%
    \else%
      \if@tempswa\setbox\beamer@tempbox=\hbox{\vbox{%
        \usebeamercolor{\beamer@colbox@color}%
        \advance\hsize by \beamer@colbox@colseps\relax%
        \advance\hsize by \beamer@colbox@colseps\relax%
        \hskip-\beamer@colbox@colseps%
        \fboxsep=0pt\colorbox{bg}{%
          \hskip\beamer@colbox@colseps%
          \hbox{\box\beamer@tempbox}%
          \hskip\beamer@colbox@colseps%
        }%
        \hskip-\beamer@colbox@colseps%
      }}\fi%
      \ifdim\@tempdima>\textwidth%
        \setbox\beamer@tempbox=\hbox to\textwidth{\hskip0pt minus\beamer@leftmargin\relax\box\beamer@tempbox\hskip0pt minus\beamer@rightmargin\relax}%
      \fi%
      \box\beamer@tempbox%
    \fi%
  \endgroup%
}
\makeatother

@@

\newlength{\inboxwd}
\newlength{\iinboxwd}
\setbeamertemplate{block alerted begin}
{
  \par\vskip\medskipamount
  \begin{beamercolorbox}[sep=0ex,rounded=true,center,dp={2.0ex}]{block alerted title}
    \vskip-0.2cm
    \usebeamerfont{block title}\large\insertblocktitle
    \vskip0.05cm
  \end{beamercolorbox}
  {\parskip0pt\par}
  \usebeamerfont{block body}
  \vskip-0.5cm
  \begin{beamercolorboxA}[sep=0.5cm, rounded=true,center]{block alerted title}
  \setlength{\inboxwd}{\linewidth}
  \addtolength{\inboxwd}{-1cm}
  \begin{beamercolorbox}[rounded=true,wd={\inboxwd},center]{block alerted body}
  \setlength{\iinboxwd}{\inboxwd}
  \addtolength{\iinboxwd}{-0.5cm}
  \begin{center}
  \begin{minipage}{\iinboxwd}
  \justifying
}

\setbeamertemplate{block alerted end}
{
  \end{minipage}
  \end{center}
  \end{beamercolorbox}
  \end{beamercolorboxA}
  \vskip\smallskipamount
}
